\documentclass{article}

    \usepackage{fancyhdr}
    \usepackage{extramarks}
    \usepackage{amsmath}
    \usepackage{amsthm}
    \usepackage{amsfonts}
    \usepackage{tikz}
    \usepackage[plain]{algorithm}
    \usepackage{algpseudocode}
    \usepackage{enumitem}
    
    \usetikzlibrary{automata,positioning}
    
    %
    % Basic Document Settings
    %
    
    \topmargin=-0.45in
    \evensidemargin=0in
    \oddsidemargin=0in
    \textwidth=6.5in
    \textheight=9.0in
    \headsep=0.25in
    
    \linespread{1.2}
    
    \pagestyle{fancy}
    \lhead{\hmwkAuthorName}
    \chead{\hmwkClass\ \hmwkTitle}
    \rhead{\firstxmark}
    \lfoot{\lastxmark}
    \cfoot{\thepage}
    
    \renewcommand\headrulewidth{0.4pt}
    \renewcommand\footrulewidth{0.4pt}
    
    \setlength\parindent{0pt}
    \setlength\parskip{0.5cm}
    
    %
    % Create Problem Sections
    %
    
    \newcommand{\enterProblemHeader}[1]{
        \nobreak\extramarks{}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
        \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
    }
    
    \newcommand{\exitProblemHeader}[1]{
        \nobreak\extramarks{Problem \arabic{#1} (continued)}{Problem \arabic{#1} continued on next page\ldots}\nobreak{}
        \stepcounter{#1}
        \nobreak\extramarks{Problem \arabic{#1}}{}\nobreak{}
    }
    
    \setcounter{secnumdepth}{0}
    \newcounter{partCounter}
    \newcounter{homeworkProblemCounter}
    \setcounter{homeworkProblemCounter}{1}
    \nobreak\extramarks{Problem \arabic{homeworkProblemCounter}}{}\nobreak{}
    
    %
    % Homework Problem Environment
    %
    % This environment takes an optional argument. When given, it will adjust the
    % problem counter. This is useful for when the problems given for your
    % assignment aren't sequential. See the last 3 problems of this template for an
    % example.
    %
    \newenvironment{homeworkProblem}[1][-1]{
        \ifnum#1>0
            \setcounter{homeworkProblemCounter}{#1}
        \fi
        \section{Problem \arabic{homeworkProblemCounter}}
        \setcounter{partCounter}{1}
        \enterProblemHeader{homeworkProblemCounter}
    }{
        \exitProblemHeader{homeworkProblemCounter}
    }
    
    %
    % Homework Details
    %   - Title
    %   - Due date
    %   - Class
    %   - Author
    %
    
    \newcommand{\hmwkTitle}{Homework\ \#1}
    \newcommand{\hmwkDueDate}{February 14, 2018}
    \newcommand{\hmwkClass}{CS 4013}
    \newcommand{\hmwkAuthorName}{\textbf{Christopher Tse}}
    
    %
    % Title Page
    %
    
    \title{
        \vspace{2in}
        \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
        \normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate}\\
        \vspace{3in}
    }
    
    \author{\hmwkAuthorName}
    \date{}
    
    \renewcommand{\part}[1]{\textbf{\large Part \Alph{partCounter}}\stepcounter{partCounter}\\}
    
    %
    % Various Helper Commands
    %
    
    % Useful for algorithms
    \newcommand{\alg}[1]{\textsc{\bfseries \footnotesize #1}}
    
    % For derivatives
    \newcommand{\deriv}[1]{\frac{\mathrm{d}}{\mathrm{d}x} (#1)}
    
    % For partial derivatives
    \newcommand{\pderiv}[2]{\frac{\partial}{\partial #1} (#2)}
    
    % Integral dx
    \newcommand{\dx}{\mathrm{d}x}
    
    % Alias for the Solution section header
    \newcommand{\solution}{\textbf{\large Solution}}
    
    % Probability commands: Expectation, Variance, Covariance, Bias
    \newcommand{\E}{\mathrm{E}}
    \newcommand{\Var}{\mathrm{Var}}
    \newcommand{\Cov}{\mathrm{Cov}}
    \newcommand{\Bias}{\mathrm{Bias}}
    
    \begin{document}
    
    \maketitle
    
    \pagebreak
    
    \begin{homeworkProblem}
        Characterize the environment for each of the following tasks, using the 9 properties listed. Justify each answer, ideally with one complete sentence.
        
        \begin{enumerate}[label=(\alph*)]
            \item \textbf{A “smart home” that autonomously controls the thermo-stat, humidifier, air-conditioner, lights, etc.}
                \begin{itemize}
                    \item Partially observable. While it could be possible to make the system fully observable with enough sensors, realistically it will not be able to detect accurate readings for the entire home.
                    
                    \item Stochastic. There is randomness involved with changes in weather, humans affecting the environment by opening/closing doors, etc.
                    
                    \item Sequential. The actions the smart home decides to take now will affect future temperatures and environment conditions.

                    \item Dynamic. The outside weather and human actions continually affect the environment as the agent thinks.

                    \item Continuous states. We deal with real values, so there are infinitely many values each reading can measure. 

                    \item Discrete actions. For the systems listed in the question, they all have two discrete states, being either on or off. While the air conditioner can be set to a range of values, it is usually a set of discrete integer temperature values.

                    \item Continuous time. In the real world, states change with the passing of time which is continuous.

                    \item Unknown physics. As far as the system is concerned, it is not aware of the physics and thermodynamics involved with controlling a home system. It only responds with an action based on the current state and the desired state. It could be argued that it is known physics since the system knows how each action will affect the environment.
                \end{itemize}
            \item \textbf{A robotic restaurant server (e.g., waiter or waitress)}
                \begin{itemize}
                    \item Partially observable. The robot server cannot see or know everything going on in the restaurant, unless a restaurant-wide vision system was implemented using cameras mounted around the room.

                    \item Stochastic. There is randomess in the needs of the restaurant patrons, and the same person may not want the same thing every time.

                    \item Episodic. Taking care of the needs on one patron should not affect others, though it could be argued that it is sequential since serving a patron one part of their meal will make them want the next (appetizer, then entree, then possibly dessert).

                    \item Dynamic. The needs of patrons can change or increase while the agent is thinking.

                    \item Continuous states. It is the real world, so there are infinitely many places the robot server could be, but the orders and needs of the patrons could be argued to be discrete since the number of things offered by the restaurant are discrete.

                    \item Continuous actions. The robot server can move its limbs at an infinite number of ways in the real world, move at an infinite number of different velocities, etc.

                    \item Continuous time. In the real world, states change with the passing of time which is continuous.

                    \item Known physics. The robot should be aware of the physics affecting it, which means it knows how to move its limbs and/or wheels in order to perform its desired actions.
                \end{itemize}

            \item \textbf{An intelligent coach that plays fantasy hockey. The coach must play in a league against other intelligent coaches, draft its team at the beginning of the season, determine which players should start or be benched each night, and potentially make trades during the season.}
                \begin{itemize}
                    \item Fully observable. The coach can see the stats of all the players before making the decisions for who to start/bench and who to trade.

                    \item Stochastic. There is randomess in the outcome of the games which is out of control of the coach.

                    \item Sequential. Making a certain move on a certain round affects following rounds. For example, if Player A was traded, it is no longer in the coach's possession to be traded in the following turns until it receives it again from another trade.

                    \item Static. The coach thinks and executes its move every night before the games proceed.

                    \item Discrete states. The states consist of the current player roster for each coach, which is a large, but infinite, number of states.

                    \item Discrete actions. The coach decides between starting or benching a player, and whether to trade a player or not.

                    \item Discrete time. The rounds take place every night during the season, and progresses by nights.

                    \item Unknown dynamics. The coach cannot know the outcome of the game based on its decision to start/bench/trade players.
                \end{itemize}

            \item \textbf{An intelligent algorithm that predicts solar flares several days in advance. The algorithm must predict (a) whether or not a solar will occur; and (b) if so, its severity (class A, B, C, M, or X)}
                \begin{itemize}
                    \item Partially observable. If the environment is the current state of the sun, it is only possible to see approximately half of it using current tools (cannot see behind it).

                    \item Stochastic. There is randomess in the chemical reactions within the sun that cannot be determined by the agent.

                    \item Episodic. Making a decision on whether a flare will happen and its severity does not affect the outcome of the next prediction.

                    \item Dynamic. The environment and reactions inside the sun are constantly changing while the agent makes its predictions.

                    \item Continuous states. The states of the reactions inside the sun are infinitely many depending on the positions and states of molecules inside the sun.

                    \item Discrete actions. The agent makes a decision from a discrete number of choices (it will happen or not, and five discrete severity classes).

                    \item Continous time. The state changes smoothly over time since it is in the real world.

                    \item Known dynamics. The dynamics are mostly known since the agent should be programmed with what conditions cause flares, and should make its predictions based on those. 
                \end{itemize}
        \end{enumerate}
    \end{homeworkProblem}

    \pagebreak

    \begin{homeworkProblem}
        Define each of the following search problems, using the 5 com-ponents listed.
        \begin{enumerate}[label=(\alph*)]
            \item \textbf{Guess which playing cards your opponent is holding in their hand (you may assume a standard 52-card deck)}
                \begin{itemize}
                    \item Inital state: You do not know any of the cards the opponent is holding.
                    
                    \item Action set: Make a set of five guesses $g_1$ to $g_5$ on the cards the opponent is holding $c_1$ through $c_5$, determine whether the guess was correct. If $g_i$ matches $c_i$, mark card as correctly guessed. Keep track of all past guesses so as to not repeat a card in the guesses. For all non-correct guesses, retry guesses. Repeat until $g_1$ through $g_5$ are correct.
                    
                    \item Transition model: A transition model would give next possible guesses by removing the current guesses and previously guessed cards from the set of cards it has left to guess.
                    
                    \item Goal test: Are guesses $g_1$ to $g_5$ all correct? 
                    
                    \item Path cost: The path cost would be determined as the number of turns needed to to correctly guess all five cards in the opponent's hand.
                \end{itemize}
            \item Find the most comfortable empty chair in a room of 1 million chairs (some chairs already have people sitting on them, and you’re not allowed to remove the current occupant!)
                \begin{itemize}
                    \item Initial state: You have not found the most comfortable empty chair in the room.
                    
                    \item Action set: Assuming the state is modeled as a set of all chairs in the room, the initial action set would be to remove from the set the chairs that are occupied. Then for each attribute in the list attributes of a comfortable chair, filter out all chairs that do not meet those requirements. Once a set of chairs remains that meet all requirements of a "comfortable chair," try each of them and select the most comfortable one.
                    
                    \item Transition model: The transition model based on this modeling of state would be the resulting set of chairs after each time the filter is run for each attribute, and then later the a set of chairs with a comfort rating during sequential trying of chairs.
                    
                    \item Goal test: Is this chair the most comfortable in the room?
                    
                    \item Path cost: The path cost can be determined by the number of chairs tried before finding the most comfortable chair.
                \end{itemize} 
            \item It’s the middle of the night, and you’re hungry. Find the nearest Tim Horton’s that is still open. 
                \begin{itemize}
                    \item Initial state: You are not at a Tim Horton's that is open.
                    
                    \item Action set: The state could be modeled as a graph with intersections being the nodes. The action set would be taking some path attached to the current node to the next node. 
                    
                    \item Transition model: The transition model for this state representation would be showing which paths are available from the next node depending on which path is taken from the current node. 
                    
                    \item Goal test: Have we arrived at a Tim Horton's that is still open?
                    
                    \item Path cost: The path cost would be determined by the total distance traveled on the roads on the way to the destination.
                \end{itemize}
        \end{enumerate}
    \end{homeworkProblem}
\end{document}